---
title: "Download the files"
author: "Joris Muller"
date: "12/18/2016"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
```

# Aim

Download the files

# Description

All the data files and the description file are available on [http://base-donnees-publique.medicaments.gouv.fr/telechargement.php](http://base-donnees-publique.medicaments.gouv.fr/telechargement.php).

Data files are *.txt*

Description file is *.pdf*

I will use `httr` to download all of them.

# Implementation

```{r}
url <- "http://base-donnees-publique.medicaments.gouv.fr/telechargement.php"
```

Get the page

```{r}
library(rvest)
library(XML)
page <- read_html(url)
```

Databases URL could be find with files ending by .txt.

These url are in link in a list (*ul*)

```{r}
dl_end_url <- page %>%
  html_nodes("#container ul a") %>%
  html_attr("href")

dl_end_url
```

We don't want to download the documentation for the moment

```{r}
# avoid the PDF
data_end_url <- dl_end_url[-grep("pdf", dl_end_url)]
```

To get the download URL, just paste the base url. 

```{r}
full_url <- function(endurl, base = url) {
  paste0(base, endurl)
}

filename <- function(endurl) {
  gsub("\\?fichier=", "", x= endurl)
}

```

We will download all the raw data in a directory

```{r}

raw_data_dir <- "raw_data"

# If the raw data was not already downloaded
if(length(dir(raw_data_dir)) == 0) {
lapply(data_end_url, 
       function(x) 
         download.file(
           url = full_url(x), 
           destfile = file.path(raw_data_dir, filename(x))
           )
  )
  
}
```

List the downloaded files 

```{r}
datafiles <- dir(raw_data_dir)
sizes <- file.size(file.path(raw_data_dir, datafiles))

kable(data.frame("File name" = datafiles, "Size (Mo)" = round(sizes / 10^6, 1), check.names = F))

```
