---
title: "Explore bdpm"
author: "Joris Muller"
date: "12/18/2016"
output: 
  html_document: 
    keep_md: yes
    self_contained: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Aim

Explore the first data set (bdpm)

# Globaly

```{r}
library(dplyr)
db <- readRDS("raw_rds/bdpm.rds")
glimpse(db)
```

# By variable

# code_cis

The *Code CIS* (Code identifiant spécialité).

Is there any duplicated value of this code ?

```{r}
any(duplicated(db$code_cis))
```

What's the range of this code ?

```{r}
range(db$code_cis)
```

# denomination

```{r}
head(db$denomination)
```

Is there some very popular drugs names I know

```{r}
grep("Doliprane", ignore.case = T, db$denomination, value = T)
```

I didn't image that there is so much kind of "Doliprane"

```{r}
amox <- grep("amoxicilline", ignore.case = T, db$denomination)
length(amox)
head(db$denomination[amox])
```

There is a lot of form of this antibiotic (152). Normal for one of the most used antibiotic.

# forme

```{r}
uforme <- unique(db$forme)
length(uforme)
```


405 various form. But there is multiple form in one line sometimes, separated by "et". Try to find the real different form.

```{r}
forms <- db$forme %>%
  strsplit(split = " et ") %>%
  unlist() 
  
length(unique(forms))  
head(forms)



```

Select the 100 most frequent

```{r}
head(as.data.frame(table(forms)))
cent <- forms %>%
  table() %>%
  as.data.frame %>%
  arrange(desc(Freq)) %>%
  head(100)
```


```{r, cache=T}
library(wordcloud2)
wordcloud2(cent)
```

